### 2021-07-05 rad-icfp-2021/correctness.tex
writing generalisation section
minor

\begin{definition}[CartSp]
    TODO, its definition and semantics of Source in it.
\end{definition}

@@

\begin{proposition}[The transpose Jacobian of !map2! and !reduce! are correct.]
    TODO
\end{proposition}

>>>>

\begin{definition}[$\CartSp$]
Let $\CartSp$ be the Cartesian category whose objects are Euclidean spaces
and whose morphisms are smooth functions between Euclidean spaces.
\MH{it's not a multicategory yet}

We can interpret Source in $\CartSp$ as follows.
    \begin{tabular}{r c l}
    $\seml \reals \semr$ &\defeq& $\RR$ \\
    $\seml$!T1xT2!$\semr$ &\defeq& $\seml$!T1!$\semr \times\seml$!T2!$\semr$ \\
    $\seml \Array{\reals}{n}\semr$ &\defeq& $\Prod_{1\leq i \leq n} \RR$ 
    \end{tabular}
A context $\Gamma=\{x_1:A_1,\ldots,x_n:A_n\}$ is interpreted as the product $\Prod_{1\leq i \leq n}\sem{A_i}$.
Well typed terms $\Gamma\vdash$!e: !$A$ are interpreted as functions $\sem{\Gamma}\to\sem{A}$. This is
routinely defined by induction on the structure of typing derivations. Constants
!c! $\reals$ are interpreted as constant functions; and the primitives operations !op1,op2!
are interpreted by composing with the corresponding functions, which are smooth. 
Variables are interpreted as $\sem{x_i}(\rho)\defeq \rho_i$. 
The remaining constructions are interpreted as follows.
\begin{tabular}{r c l}
    $\seml$!map2 (x,y.e1) e2 e3!$\semr$ &=& TODO\\
    $\seml$!reduce (x,y.e1) e2 e3!$\semr$ &=& TODO
\end{tabular}
\end{definition}

@@

\begin{proposition}[The transpose Jacobian of map2 and reduce are correct.]
    TODO
\end{proposition}
